Regression Analysis—Simple

### 2019-02-25 figures/author_outcomes/submission_outcome_by_gender.rmd

# converts a provided p-value into a representation that is easier to visualize
sig2ast <- function(p) { ifelse(p <= 0.0001, "****", 
                                ifelse(p <= 0.001, "***", 
                                       ifelse(p <= 0.01, "**", 
                                              ifelse(p <= 0.05, "*", 
                                                     ifelse(p < 0.1, ".", "ns")
                                              )
                                       )
                                )
                          )
}

@@

gender_outcomes <- data %>%
  ggplot(aes(x = gender, y = measurement, color = factor(gender), shape = factor(gender), fill = factor(gender))) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, color = "black") +
  geom_text(aes(x = 1.5, y = 0.89, label = ifelse(measure_key == "Submissions", "", as.character(sig))), color = "black") +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  #facet_grid(author_key ~ measure_key) +
  facet_wrap(~author_key) +
  coord_cartesian(ylim = c(0, 1.0)) +
  theme_dakota() +
  guides(fill = F) +
  labs(
    x = "Gender of Author",
    y = "% of full submissions accepted"
  )

@@

p1 <- data_national_p1 %>%
  # Start ggplot
  ggplot(aes(x = ca_country, y = prop)) +
  geom_bar(stat = "identity", color = "black", alpha = 0.8, fill = "dodgerblue4", position = position_dodge(1)) +
  geom_text(aes(y = prop, label = paste0(round(prop, 3) * 100, "%")), size = 2.5, hjust = -0.2, family = "Times", position = position_dodge(1)) +
  scale_y_continuous(limits = c(0, 1)) +
  facet_wrap(~prop_key, labeller = labeller(key = labels)) +
  theme_dakota() +
  coord_flip() +
  ylim(0, 0.7) +
  labs(y = "") +
  theme(
    strip.background = element_blank(),
    text = element_text(size = 10, family = "Times"),
    plot.title = element_text(size = 12),
    strip.text = element_text(face = "bold"),
    axis.title.y = element_blank()
  )

data_national_p2 <- elife %>%
  filter(initial_decision_made & (full_decision_made | full_decision_date_isNA) & !is.na(ca_country)) %>%
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>% # capitalize first letter of country stirngs
  group_by(ca_country) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_count = sum(encouraged == TRUE, na.rm = T),
    encourage_rate = encourage_count / paper_count,
    accept_rate = accept_count / sum(!has_full_submission | full_decision_made, na.rm = T),
    encourage_accept_rate = accept_count / sum(has_full_submission & full_decision_made, na.rm = T)
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  top_n(8, totals) %>%
  mutate(
    ca_country = reorder(ca_country, encourage_rate)
  ) %>%
  gather(measure_key, value = measurement, encourage_rate, accept_rate, encourage_accept_rate) %>%
  mutate(measure_key = factor(measure_key, 
                           levels = c("encourage_rate", "encourage_accept_rate", "accept_rate"),
                           labels = c("encourage_rate" = "% of initial submissions encouraged", 
                                      "encourage_accept_rate" = "% of full submissions accepted",
                                      "accept_rate" = "% of initial submissions accepted"
                                      ))
  ) %>%
  group_by(measure_key) %>%
  mutate(
    se = 1.96 * sqrt(measurement * (1 - measurement) / paper_count),
    lower = measurement - se,
    upper = measurement + se
  )

p2 <- data_national_p2 %>%
  ggplot(aes(x = ca_country, y = measurement)) +
  geom_bar(stat = "identity", color = "black", fill = "dodgerblue4", alpha = 0.8) +
  geom_text(aes(y = measurement, label = paste0(round(measurement, 3) * 100, "%")), size = 2.5, hjust = -0.6, family = "Times") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  facet_wrap(~measure_key, labeller = labeller(key = labels)) +
  theme_dakota() +
  labs(y = "%") +
  coord_flip() +
  ylim(0, 0.7) +
  theme(
    axis.title.y = element_blank()
  ) +
  labs(y = "")

@@

## Save the file
```{r}
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = g, height = 5, width = 11)
```

>>>>

# converts a provided p-value into a representation that is easier to visualize
sig2ast <- function(p) { ifelse(p <= 0.0001, "***", 
                                ifelse(p <= 0.001, "***", 
                                       ifelse(p <= 0.01, "**", 
                                              ifelse(p <= 0.05, "*", 
                                                     ifelse(p < 0.1, "•", "ns")
                                              )
                                       )
                                )
                          )
}

@@

gender_outcomes <- data %>%
  ggplot(aes(x = gender, y = measurement, color = factor(gender), shape = factor(gender), fill = factor(gender))) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, color = "black") +
  geom_text(aes(x = 1.5, y = 0.89, label = ifelse(measure_key == "Submissions", "", as.character(sig))), color = "black", size = 4) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_wrap(~author_key) +
  coord_cartesian(ylim = c(0, 1.0)) +
  theme_dakota() +
  guides(fill = F) +
  labs(
    x = "Gender of Author",
    y = "% of full submissions accepted",
    title = "A"
  ) +
  theme(plot.title = element_text(size = 18))

@@

p1 <- data_national_p1 %>%
  # Start ggplot
  ggplot(aes(x = ca_country, y = prop)) +
  geom_bar(stat = "identity", color = "black", alpha = 0.8, fill = "dodgerblue4", position = position_dodge(1)) +
  geom_text(aes(y = prop, label = paste0(round(prop, 3) * 100, "%")), size = 2.5, hjust = -0.2, family = "Times", position = position_dodge(1)) +
  scale_y_continuous(limits = c(0, 1)) +
  facet_wrap(~prop_key, labeller = labeller(key = labels)) +
  theme_dakota() +
  coord_flip() +
  ylim(0, 0.7) +
  labs(y = "",
       title = "B") +
  theme(
    strip.background = element_blank(),
    text = element_text(size = 10, family = "Times"),
    plot.title = element_text(size = 18),
    strip.text = element_text(face = "bold"),
    axis.title.y = element_blank()
  )

data_national_p2 <- elife %>%
  filter(initial_decision_made & (full_decision_made | full_decision_date_isNA) & !is.na(ca_country)) %>%
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>% # capitalize first letter of country stirngs
  group_by(ca_country) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_count = sum(encouraged == TRUE, na.rm = T),
    encourage_rate = encourage_count / paper_count,
    accept_rate = accept_count / sum(!has_full_submission | full_decision_made, na.rm = T),
    encourage_accept_rate = accept_count / sum(has_full_submission & full_decision_made, na.rm = T)
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  top_n(8, totals) %>%
  mutate(
    ca_country = reorder(ca_country, encourage_rate)
  ) %>%
  gather(measure_key, value = measurement, encourage_rate, accept_rate, encourage_accept_rate) %>%
  mutate(measure_key = factor(measure_key, 
                           levels = c("encourage_rate", "encourage_accept_rate", "accept_rate"),
                           labels = c("encourage_rate" = "% of initial sub. encouraged", 
                                      "encourage_accept_rate" = "% of full sub. accepted",
                                      "accept_rate" = "% of initial sub. accepted"
                                      ))
  ) %>%
  group_by(measure_key) %>%
  mutate(
    se = 1.96 * sqrt(measurement * (1 - measurement) / paper_count),
    lower = measurement - se,
    upper = measurement + se
  )

p2 <- data_national_p2 %>%
  ggplot(aes(x = ca_country, y = measurement)) +
  geom_bar(stat = "identity", color = "black", fill = "dodgerblue4", alpha = 0.8) +
  geom_text(aes(y = measurement, label = paste0(round(measurement, 3) * 100, "%")), size = 2.5, hjust = -0.6, family = "Times") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  facet_wrap(~measure_key, labeller = labeller(key = labels)) +
  theme_dakota() +
  labs(y = "%") +
  coord_flip() +
  ylim(0, 0.7) +
  theme(
    axis.title.y = element_blank(),
    plot.title = element_text(size = 18)
  ) +
  labs(y = "",
       title = "C")

@@

## Save the file
```{r}
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = g, height = 7, width = 10)
```

### 2019-02-25 figures/regression_analysis/regression_analysis_interaction.rmd

### Construct the initial regression plot
```{r}
initial_reg_plot <- plot_model(initial_model, 
           vline.color = "black", 
           sort.est = TRUE, 
           show.values = TRUE, 
           value.offset = .3, 
           axis.labels = initial.cov.labels,
           wrap.labels = 100, # basically, don't wrap the labels, squeeze them all in
           title = "Encouragement of initial submissions",
           axis.lim = c(0.1, 10)) +
  theme_bw()

@@

### Construct the plot for full submissions
```{r}
full.cov.labels = c("submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "fa_genderM" = "First Author is Male",
               "fa_genderUNK" = "First Author is Unknown Gender",
               "la_institution_rankTop" = "Last Author Inst. Top",
               "la_continentAfrica" = "Last author from Africa",
               "la_continentAsia" = "Last author from Asia",
               "la_continentEurope" = "Last author from Europe",
               "la_continentOceania" = "Last author from Oceania",
               "la_continentSouth America" = "Last author from South America",
               "I(la_reviewer_dist/1e+06)" = "Sum of geographic distance (1000s km)",
               "la_reviewer_dist_zeroTRUE" = "Sum of geographic distance is zero",
               "author_reviewer_interactionFemale Author, All Women" = "Last author female - all reviewers female",
               "author_reviewer_interactionFemale Author, Mixed" = "Last author female - mixed reviewers",
               "author_reviewer_interactionMale Author, All Men" = "Last author male - all reviewers male",
               "author_reviewer_interactionMale Author, All Women" = "Last author male - all reviewers female",
               "author_reviewer_interactionMale Author, Mixed" = "Last author male - mixed reviewers"
               )

@@

```{r}
full_reg_plot <- plot_model(full_model, 
           vline.color = "black", 
           rm.terms = c("fa_genderUNK"),
           sort.est = TRUE, 
           show.values = TRUE, 
           value.offset = .4, 
           axis.labels = full.cov.labels,
           wrap.labels = 100, # basically, don't wrap the labels, squeeze them all in
           title = "Acceptance of full submissions",
           axis.lim = c(0.1, 10)) +
  theme_bw()

>>>>

### Construct the initial regression plot
```{r}
initial_reg_plot <- plot_model(initial_model, 
           vline.color = "black", 
           sort.est = TRUE, 
           show.values = TRUE, 
           value.offset = .3, 
           axis.labels = initial.cov.labels,
           wrap.labels = 100, # basically, don't wrap the labels, squeeze them all in
           title = "A. Encouragement of initial submissions",
           axis.lim = c(0.1, 10)) +
  theme_bw()

@@

### Construct the plot for full submissions
```{r}
full.cov.labels = c("submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "fa_genderM" = "First Author is Male",
               "fa_genderUNK" = "First Author is Unknown Gender",
               "la_institution_rankTop" = "Last Author Inst. Top",
               "la_continentAfrica" = "Last author from Africa",
               "la_continentAsia" = "Last author from Asia",
               "la_continentEurope" = "Last author from Europe",
               "la_continentOceania" = "Last author from Oceania",
               "la_continentSouth America" = "Last author from South America",
               "I(la_reviewer_dist/1e+06)" = "Sum of geo. distance (1000s km)",
               "la_reviewer_dist_zeroTRUE" = "Sum of geo. distance is zero",
               "author_reviewer_interactionFemale Author, All Women" = "Last author female - all rev. female",
               "author_reviewer_interactionFemale Author, Mixed" = "Last author female - mixed rev.",
               "author_reviewer_interactionMale Author, All Men" = "Last author male - all rev. male",
               "author_reviewer_interactionMale Author, All Women" = "Last author male - all rev. female",
               "author_reviewer_interactionMale Author, Mixed" = "Last author male - mixed rev."
               )

@@

```{r}
full_reg_plot <- plot_model(full_model, 
           vline.color = "black", 
           rm.terms = c("fa_genderUNK"),
           sort.est = TRUE, 
           show.values = TRUE, 
           value.offset = .4, 
           axis.labels = full.cov.labels,
           wrap.labels = 100, # basically, don't wrap the labels, squeeze them all in
           title = "B. Acceptance of full submissions",
           axis.lim = c(0.1, 10)) +
  theme_bw()

### 2019-02-25 figures/regression_analysis/regression_analysis_simple.rmd

### Plot the regression estimates for the initial submissions model
```{r}
initial_reg_plot <- plot_model(initial_model, 
           vline.color = "black", 
           #rm.terms = c("ca_genderUNK"),
           sort.est = TRUE, 
           show.values = TRUE, 
           value.offset = .3, 
           axis.labels = initial.cov.labels,
           wrap.labels = 100, # basically, don't wrap the labels, squeeze them all in
           title = "Encouragement of initial submissions",
           axis.lim = c(0.1, 10)) +
  theme_bw()

@@

### Plot the regression estimates for full submissions
```{r}
full_reg_plot <- plot_model(full_model, 
           vline.color = "black", 
           sort.est = TRUE, 
           show.values = TRUE, 
           value.offset = .3, 
           axis.labels = full.cov.labels,
           wrap.labels = 100, # basically, don't wrap the labels, squeeze them all in
           title = "Acceptance of full submissions",
           axis.lim = c(0.1, 10)) +
  theme_bw()

>>>>

### Plot the regression estimates for the initial submissions model
```{r}
initial_reg_plot <- plot_model(initial_model, 
           vline.color = "black", 
           #rm.terms = c("ca_genderUNK"),
           sort.est = TRUE, 
           show.values = TRUE, 
           value.offset = .3, 
           axis.labels = initial.cov.labels,
           wrap.labels = 100, # basically, don't wrap the labels, squeeze them all in
           title = "A. Encouragement of initial submissions",
           axis.lim = c(0.1, 10)) +
  theme_bw()

@@

### Plot the regression estimates for full submissions
```{r}
full_reg_plot <- plot_model(full_model, 
           vline.color = "black", 
           sort.est = TRUE, 
           show.values = TRUE, 
           value.offset = .3, 
           axis.labels = full.cov.labels,
           wrap.labels = 100, # basically, don't wrap the labels, squeeze them all in
           title = "B. Acceptance of full submissions",
           axis.lim = c(0.1, 10)) +
  theme_bw()
